Data Flow Analysis\\in the Presence of Correlated Calls

### 2014-12-03 content/datastr.tex
moving more stuff to appendix

\subsubsection{Efficiency}\label{sec:efficiency}
In this section, we will show that our representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
\begin{lemma}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient.
\end{lemma}
\begin{proof}
\leavevmode
  \begin{enumerate}
    \item The identity function is represented as
      \[
        \denote{\id}=\{(r,\,\langle \bot_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,;
      \]
      the top function is represented as
      \[
        \denote{\lambda m\,.\,\topcc}=\{(r,\,\langle \top_T,\,\top_T\rangle)\,|\,r\in \rcc\}\,.
      \]
    \item Equations~\eqref{eq:compclosed} and~\eqref{eq:meetclosed} show that the representation of micro functions is closed under composition and meet.
    \item To show that our representation for micro functions forms a lattice with finite height, let us first show that $\lcc_\rcc:\,\rcc\to2^T$ forms a lattice. Since $T$ is a finite set, $(2^T,\,\subseteq)$ is a finite-height lattice. $\rcc$ is a finite set. Hence, the mapping
    \[
      \rcc\mapsto2^T=\{(r,\,t)\,|\,r\in \rcc,\,t\in 2^T\}=\lcc_\rcc
    \]        
    also forms a finite-height lattice \cite{nielson1999principles}.

    Furthermore, $\lcc_\rcc$ is a finite set. 
    Every element of $\lcc_\rcc$ can be applied to $|\rcc|$ receivers, where each receiver is mapped to a set of types. There are $|\rcc|\cdot2^{|T|}$ different possibilities to form those mappings, so
    \[
      |\lcc_\rcc|=|\rcc|\cdot2^{|T|}.
    \]
    Therefore, $\lcc_\rcc\mapsto \lcc_\rcc$ also forms a finite-height lattice.
    \item All operations can be computed in $O(\rcc\times T)$ time. Note that the $\rcc$ and $T$ sets are an input to the correlated-calls analysis, and the time it takes to compute the meet or composition of micro functions is independent of the representation of the specific operand micro functions.
    \item The space bound is $O(\rcc\times T)$.
  \end{enumerate}
\end{proof}

>>>>

The following Lemma states that the representation of micro functions is efficient according to the definition  of efficiency discussed in Section~\ref{sec:ccdatastr}.
\begin{lemma}\label{lem:efficient}
  The correlated-call representation of a micro function is efficient.
\end{lemma}

### 2014-12-03 content/intro.tex
started to move proofs to appendix; removing dependency on minted
moving more stuff to appendix

For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in line~\ref{line:newa} is \verb'A' or \verb'B'.
The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
A concrete execution path for the main method might therefore go through \verb'A.foo' and \verb'A.bar', or through \verb'B.foo' and \verb'B.bar'.
However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.

  \begin{listing}[h]
    \inputMinted{java}{ccexample.java}
    \caption{Example program containing correlated calls}
    \label{list:ccexample}
  \end{listing}

>>>>

For example, in Listing~\ref{list:ccexample}, it is not possible to infer statically whether the runtime type of the variable \verb'a' in the \texttt{main} method is \verb'A' or \verb'B'.
The call \verb'a.foo()' can be dispatched to either \verb'A.foo' or \verb'B.foo', and \verb'a.bar(v)' can be dispatched to either \verb'A.bar' or \verb'B.bar'.
A concrete execution path for the main method might therefore go through \verb'A.foo' and \verb'A.bar', or through \verb'B.foo' and \verb'B.bar'.
However, there cannot be an execution path through \verb'A.foo' and \verb'B.bar' or through \verb'B.foo' and \verb'A.bar'.

\begin{figure}
  \centering
  \begin{minipage}{\textwidth}
    \inputMinted{java}{ccexample.java}
  \end{minipage}
  \caption{Example program containing correlated calls}
  \label{list:ccexample}
\end{figure}
